---
title: "Ethos Engage 
Methamphetamine Use"
output: 
  flexdashboard::flex_dashboard:
    # theme: journal
    # source_code: embed
    # orientation: columns
    # theme: journal
      # version: 4
      # bootswatch: journal
    # social: menu
    # source_code: embed
    # self_contained: TRUE
---


```{r}
#| label: load-packages
#| message: false

library(flexdashboard)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
library(thematic)
thematic::thematic_rmd()
library(flexdashboard)
library(tidyverse)
library(readxl)
library(scales)
library(DT)
library(gt)
library(finalfit)
library(dplyr)
library(forcats)
library(tidyr)
library(ggplot2)
library(here)
library(RColorBrewer) 
library(leaflet)
library(leaflet.extras)
library(sf)
library(here)

# if (FALSE) {

library(rmarkdown)
library(flexdashboard)

# simple invocation
# render("ethos-methamphetamine-dashboard.Rmd", flex_dashboard())

# specify the theme option
# render("ethos-methamphetamine-dashboard.Rmd", flex_dashboard(theme = "journal"))
# }




# you can get marmap from CRAN, but to get the latest brew, try github:
# install.packages("promises")
# install.packages("devtools") # just do this once
# library(devtools) # load library devtools
# install_github("ericpante/marmap@marmap-v0.9") # install from github

# theme_set(theme_minimal(base_size = 24, base_family = "Atkinson Hyperlegible"))
```

#  {.sidebar}

**Title:** Sociodemographic and behavioural characteristics associated with methamphetamine use among participants enrolled in ETHOS Engage.

**Description:** Enhancing Treatment of Hepatitis C in Opioid Substitution Settings (ETHOS) Engage is a national observational cohort study of people who have a history of injecting drug use, and report injecting drug use in the preceding six months or are currently receiving OAT (comprising methadone, buprenorphine, and buprenorphine-naloxone in Australia) Participants were enrolled across two recruitment waves. During Wave 1 (May 2018- September 2019) recruitment occurred in 25 sites, including drug treatment clinics (n=21) and needle and syringe programs (NSPs) (n=4). During Wave 2 (November 2019-June 2021), participants were recruited from 21 of the 25 sites which participated in Wave 1, including drug treatment clinics (n=19) and NSPs (n=2) (Overall, 2,395 unique participants were enrolled: 1,443 participants enrolled during 2018-2019 (Wave 1) and 1,211 enrolled during 2019-2021 (Wave 2) (259 participated in b

**Methods:** To be included in this analysis, participants had to report prescribed or non-prescribed opioid use in the preceding six months or have received OAT in the preceding six months. pioid use was defined as use of prescribed or non-prescribed opioids and/or extra-medical (injection and/or non-prescribed) use of methadone/buprenorphine. Stimulant use was defined as use of cocaine or amphetamines.

**Study Oversight** The study protocol was approved by the Human Research Ethics Committees at St Vincent’s Hospital, Sydney, and the Aboriginal Health and Medical Research Council (HREC Ref: HREC/17/ SVH/113).

::: {.callout-note collapse="true"}

**Disclaimer**

These data are not final and are not publicly available yet.

:::

<!-- ------------------------------------------------------------------------ -->
# Map of sampling locations


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r load-libraries, include=FALSE}

# LOAD LIBRARIES ----------------------------------------------------------
library(RColorBrewer) 
library(leaflet)
library(leaflet.extras)
library(sf)
library(here)
library(usethis)
library(ggmap)
library(ggplot2)
library(pacman)
library(dplyr)
library(knitr)
library(DT)
library(viridis)
library(ggplot2)
library(reticulate)
library(rmarkdown)
library(flexdashboard)
library(readxl)
library(gt)
library(gtsummary)
library(flextable)
library(sf)

# my_packages <- c("tidyverse", "broom", "coefplot", "cowplot",
#                  "gapminder", "GGally", "ggrepel", "ggridges", "gridExtra",
#                  "here", "interplot", "margins", "maps", "mapproj",
#                  "mapdata", "MASS", "quantreg", "rlang", "scales",
#                  "survey", "srvyr", "viridis", "viridisLite", "devtools")
# 
# install.packages(my_packages, repos = "http://cran.rstudio.com")
# devtools::install_github("kjhealy/socviz")

# usethis::create_github_token()
# 
# gitcreds::gitcreds_set()

```

```{r load-data, include = FALSE}
# LOAD DATASETS -----------------------------------------------------------

load(
  here::here("Data", "Processed", "ethos_all_factors.rda")
)

load(
  here::here("Data", "Processed", "ethos_final_analysis.rda")
)

load(
  here::here("Data", "Processed", "ethos_all_factors.rda")
)

# Primary Health Networks 
shape <- read_sf(dsn = "C:/Users/Mjstowe/mjstowe-projects/ethos-stimulants/Data/Input", layer = "Primary_Health_Networks")

# NSW Local Health Districts (LHD)
nsw_lhd <- read_sf(dsn = "Data/Input", layer = "NSW_LHD_Boundaries")%>%
  sf::st_as_sf(coords = c("lat", "lon"), # columns with geometry
               crs = 4326) 

# Locations of participating sites 
ethos.loc <- read_csv("Data/Input/ethos_locations.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), remove = FALSE)
```

```{r, echo=FALSE}




# shape <- shape %>%
  # st_transform(crs = 4326)


# ethos.loc <- read.csv("C:/Users/Mjstowe/OneDrive - UNSW/04_projects/04-archived/projects/ETHOS Engage/sub-studies/OAT preference/analysis/data/raw_data/ethos_locations.csv") %>%
  # st_as_sf(coords = c("Longitude", "Latitude"), remove = FALSE)

my.pal2 = brewer.pal(n=7, "GnBu")

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = my.pal2
)


l <- leaflet(shape) %>%
  
  addTiles() %>%
  enableMeasurePath() %>%
  addMeasurePathToolbar(options = measurePathOptions(imperial = FALSE,
                                                     minPixelDistance = 100,
                                                     showDistances = FALSE,
                                                     showOnHover = TRUE))%>%
  
  # addPolygons(data = shape,
  #             # weight defines how thick the borders will be for our boundaries 
  #             # (the larger this number, the thicker the lines will become)
  #             weight = 2, 
  #             color = "black", 
  #             dashArray = " ", # makes the boundary lines solid (by default)
  #             # fillColor = ~pal(Secondary$latest_year_enrolment_FTE), 
  #             smoothFactor = 0.5,
  #             opacity = 1.0,
  #             fillOpacity = 0.5,
  #             # the boundary lines will turn thick red when we hover over it
  #             highlightOptions = highlightOptions(color = "red", 
  #                                                 weight = 3, 
  #                                                 bringToFront = TRUE))%>%
  addAwesomeMarkers(lat=ethos.loc$Latitude,
                    lng=ethos.loc$Longitude, 
                    label=ethos.loc$Site, 
                    icon=icons,
                    clusterOptions = markerClusterOptions()) 
    # addLegend(labels=ethos.loc$Site, values=ethos.loc, opacity=0.9, title = "Sampling locations", position = "bottomleft", colors=ethos.loc$Site)


esri <- grep("^Esri", providers, value = TRUE)

for (provider in esri) {
  l <- l %>% addProviderTiles(provider, group = provider)
}

l %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = TRUE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomleft") %>%
  
    # add scale bar
  # addMeasure(position = "topright",
  #            primaryLengthUnit = "meters",
  #            primaryAreaUnit = "sqmeters",
  #            activeColor = "#3D535D",
  #            completedColor = "#7D4479") %>%
  
  htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
        })
    }")

# l

  
# save the widget in a html file if needed.
# library(htmlwidgets)
# saveWidget(l, file=paste0( getwd(), "/HtmlWidget/choroplethLeaflet5.html"))

```


# Summary statistics

```{r, echo=FALSE}


data <- data %>%
  mutate(meth_roa = fct_relevel(meth_roa, "Inject methamphetamine", "Smoke methamphetamine", "Don't use methamphetamine"))


summary_pts <-
  data %>%
  # filter(prefer.treat.yn=="Yes" | prefer.treat.yn=="No")%>%
  # filter(inclusion==1)%>%
  tbl_summary(by=meth_roa, include = c(waves, surveyage, age_group, age_45, 
                          genderall.factor, indigenous,  homeless.fct,  year10,
                          prison.6month, income,hazard_alc, drug_injected_1m, 
                          heroin_inj, heroin_noninj, methadone_inj,
                          methadone_noninj, bupe_inj,
                          bupe_noninj, otheropi_inj,
                          otheropi_noninj, morph_inj,
                          morph_noninj, fent_inj,
                          fent_noninj, amphet_inj,
                          amphet_noninj, coke_inj,
                          coke_noninj, benzo_inj,
                          benzo_noninj,drug_injected_1m, injectdrug.month,
                          injectdrug.group.month,injectfreq.month, 
                          injectfreq.month.daily,injectdays.month,oat_current.yn,oat.ever.yn,    
                          oat_history, oatdur, dose.satisfied, dose.takeaways.yn,
                           overdoseopi_12m,naloxone_train, naloxone_access,
                          hcvab_status, health.pain, hcvrna_tested, hcv_ever_treat, hcv_testresult,
                          hcvrna_current,hcvab_status, 
                          health.pain,stigma.inject.yn,  stigma.inject, stigma.hcv, stigma.hcv.yn,
                          discrim, discrim.yn, 
                          oat.ever.yn,  site_name, aria.x, state),
  # type = all_categorical() ~ "categorical",
label =
                list(state ~"State",
                     surveyage ~ "Age",
                     year10 ~ "Level of formal education",
                     age_group ~ "Age group",
                     injectdrug.group.month ~ "Drug class injected in the last month",
                     injectdays.month ~ "Number of days injected in the last month"
                     ),
              type = all_categorical()~"categorical",
              missing = "no",
              percent = "row",
              statistic =(all_continuous()  ~ "{median} ({p25} - {p75})"))%>%
  add_stat_label()%>%
  add_overall(statistic = list(all_continuous()  ~ "{median} ({p25} - {p75})",
                               all_categorical() ~ "{n}")) %>%
  modify_footnote(update = everything() ~ NA, abbreviation = FALSE) %>%
  modify_header(
    stat_0 = '**Overall** \n **(n = {n})**',
    stat_1 = '**Inject methamphetamine** \n **(n = {n})**',
    stat_2 = '**Smoke methamphetamine** \n **(n = {n})**',
    stat_3 = '**Do not use methamphetamine** \n **(n = {n})**'
  ) %>%
    # remove_row_type(variable = injectdrug.group.month,
    #               type = "level", level_value = "Other")%>%
  bold_labels()

summary_pts.kable <- summary_pts %>%
   gtsummary::as_kable_extra(
    format = "html",
    booktabs = TRUE,
    longtable = TRUE,
    linesep = "",
    caption="Table 1. Demographic and behavioural characteristics of all participants enrolled in this study stratified by injecting, smoking and none use of methamphetamine across Waves I & II of ETHOS Engage")%>%
  kableExtra::kable_styling(
      position = "left",
      latex_options = c("striped", "repeat_header"),
      stripe_color = "gray!15"
    )%>%
    kableExtra::scroll_box(
  # height = "50%",
  # width = "100%",
  box_css = "border: 1px solid #ddd; padding: 5px; ",
  extra_css = NULL,
  fixed_thead = TRUE
)


summary_pts.kable

```

# Data dictionary and summary

```{r, warning="false", message="false", include="FALSE"}
#| title: Table 1. Dataset of people who inject, smoke or do not use methamphetamine enrolled across both waves.
#| echo: false
#| include: true



library(qreport)
library(summarytools)
# 
# dataOverview(data)

methamphetamine_dataset <- data %>%
  filter(inclusion==1)%>%
  dplyr::select(prefer.treat.yn:hcvrna_current)


```


```{r summary, results='asis'}
print(dfSummary(methamphetamine_dataset
                ), method = 'render')
```

<!-- # Dataset -->

```{r}

# 
# font.size <- "10pt"
# 
# table <- methamphetamine_dataset|>
#   arrange(methamphetamine_dataset) |>
#   DT::datatable(
#     options = list(
#       initComplete = htmlwidgets::JS(
#           "function(settings, json) {",
#           paste0("$(this.api().table().container()).css({'font-size': '", font.size, "'});"),
#           "}"),
#       dom = "lrtip",
#       paging = TRUE,
#       buttons=c("copy","print","pdf","csv"),
#       # lengthMenu = c(20, 100, 175),
#       # pageLength = 10,
#       scrollY = TRUE),
#       filter="top",
#     rownames=TRUE,
#     caption="Table: Dataset of people who inject or smoke, or don't use methamphetamine across Wave I & II of ETHOS Engage"
#   )
# 
# table
```
